\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% Define custom colors
\definecolor{maincolor}{RGB}{25, 25, 112} % Navy/Indigo color
\definecolor{sectioncolor}{RGB}{25, 25, 112} % Navy/Indigo for section headers
\definecolor{subheadingcolor}{RGB}{25, 25, 112} % Navy/Indigo for subheadings
\definecolor{datecolor}{RGB}{100, 100, 100} % Dark gray for dates

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting with custom color
\titleformat{\section}{
  \vspace{0pt}\scshape\raggedright\large\bfseries\color{sectioncolor}
}{}{0em}{}[\titlerule \vspace{2pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small\color{datecolor} #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

% Modified command for education without dates
\newcommand{\resumeEducation}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \\
      \textit{\small#2} & \textit{\small #3} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----start----
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape \textcolor{maincolor}{Pooja Patel}} \\ \vspace{10pt}
    \small 
    \raisebox{-0.1\height}\faPhone\ \textcolor{subheadingcolor}{+91 9023562773} ~ 
    \href{mailto:poojaspatel1375@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \textcolor{subheadingcolor}{\underline{poojaspatel1375@gmail.com}}} ~ 
    \href{https://www.linkedin.com/in/pooja-p-77329933b/}{\raisebox{-0.2\height}\faLinkedin\ \textcolor{subheadingcolor}{\underline{/poojapatel}}}  ~
    \href{https://github.com/PoojasPatel013}{\raisebox{-0.2\height}\faGithub\ \textcolor{subheadingcolor}{\underline{/poojapatel013}}}  ~
    \href{https://poojaxdev.vercel.app/}{\raisebox{-0.2\height}\faGlobe\ \textcolor{subheadingcolor}{\underline{pooja.dev}}}
\end{center}
\vspace{-14pt}


%-----------PROFILE-----------
\section{Profile}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item{
Detail-oriented and passionate Computer Science student specializing in cloud architectures, Cloud Security, networking, and full-stack web development. Actively engaged in cloud ecosystems such as Google Cloud, AWS, Azure, and OCI, with proficient experience working with Cloud Shell. Adept in building curated, user-focused websites and currently exploring mobile development with Android. A published author of two globally available books, combining creativity with technology. Strong advocate for purposeful innovation and national service, aspiring to serve in the Indian Armed Forces through the SSB pathway.
}

\end{itemize}



%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
  {Pregard}{Jul 2023-Oct 2023}
  {Basics of CyberSecurity - Trainee}{Remote}
  \resumeItemListStart
    \resumeItem{Gained hands-on experience in ethical hacking, Kali Linux, Windows access control and security breach prevention.}
    \resumeItem{Implemented firewall rules and network security protocols to safeguard sensitive data.}
   \resumeItem{Gained practical understanding of OS management by configuring and exploring key system functionalities across Linux and Windows, including process handling, user permissions, and system architecture.}

  \resumeItemListEnd

%-----------RELEVANT PROJECTS-----------
\section{Projects}
   \vspace{-5pt}
   \resumeSubHeadingListStart
         \resumeProjectHeading
{\textbf{\href{https://github.com/PoojasPatel013}{\textcolor{maincolor}{Desifusion}}} $|$ \emph{Template Engine, Node.js, MongoDB}}{}
\vspace{-8pt}
\resumeItemListStart 
  \resumeItem{Designed and developed a recipe preservation platform to highlight traditional Indian cuisine using Node.js and a custom template engine.}
  \resumeItem{Created a categorized recipe JSON schema and integrated MongoDB for scalable data storage and efficient querying.}
  \resumeItem{Implemented search, filter, and regional tagging features to improve user discovery and engagement.}
\resumeItemListEnd 
\vspace{-8pt}

\resumeProjectHeading
{\textbf{\href{https://github.com/PoojasPatel013}{\textcolor{maincolor}{Dive\` - Luxury Collection Platform}}} $|$ \emph{Express, React, API, MongoDB}}{}
\vspace{-8pt}
\resumeItemListStart
  \resumeItem{Built a full-stack luxury fashion e-commerce platform with React and Express, targeting premium European brands.}
  \resumeItem{Used RESTful APIs for product data handling and integrated MongoDB for inventory and user management.}
\resumeItemListEnd 
\vspace{-8pt}

\resumeProjectHeading
{\textbf{\href{https://github.com/PoojasPatel013}{\textcolor{maincolor}{Weather Dashboard}}} $|$ \emph{API, Express, Socket.io}}{}
\vspace{-8pt}
\resumeItemListStart
  \resumeItem{Created a real-time weather app that displays accurate forecasts using external APIs and real-time socket updates.}
  \resumeItem{Integrated an AI-based suggestion module for clothing based on live temperature, humidity, and wind conditions.}
\resumeItemListEnd 
\vspace{-8pt}

\resumeProjectHeading
{\textbf{\href{https://github.com/PoojasPatel013}{\textcolor{maincolor}{Digital Art Gallery}}} $|$ \emph{API, React, Canvas, Three.JS}}{}
\vspace{-8pt}
\resumeItemListStart
  \resumeItem{Built a 3D digital art showcase using Three.js to enable immersive navigation through virtual gallery rooms.}
  \resumeItem{Integrated Canvas for real-time painting previews and custom zoom/pan controls.}
\resumeItemListEnd 
\vspace{-8pt}

\resumeProjectHeading
{\textbf{\href{https://github.com/PoojasPatel013}{\textcolor{maincolor}{FemPlan}}} $|$ \emph{API, Flask, Bootstrap, Python}}{}
\vspace{-8pt}
\resumeItemListStart
  \resumeItem{Engineered a women-centric productivity and wellness app with modules for menstrual cycle tracking, health tips, and journaling.}
  \resumeItem{Used Flask to create backend services and DSA algorithms for personalized habit tracking and reminders.}
  \resumeItem{Applied Bootstrap for UI responsiveness and Python for cycle prediction using historical data.}
\resumeItemListEnd 
\vspace{-8pt}

\resumeProjectHeading
{\textbf{\href{https://github.com/PoojasPatel013}{\textcolor{maincolor}{ChronoVault}}} $|$ \emph{API, MERN, AI Integration}}{}
\vspace{-8pt}
\resumeItemListStart
  \resumeItem{Developed a community-based mental wellness platform offering AI-guided therapy, journaling, and lifestyle tracking.}
  \resumeItem{Integrated GPT-powered conversational AI to assist users in therapeutic self-reflection and mood processing.}
  \resumeItem{Enabled human consultancy support and a peer-driven communal space for mental health discussions and exercises.}
  \resumeItem{Included mental health activities, goal setting, and personalized wellness reports to track healthy habits over time.}
\resumeItemListEnd 
\vspace{-8pt}

\resumeProjectHeading
{\textbf{\href{https://github.com/PoojasPatel013}{\textcolor{maincolor}{Mood Journal}}} $|$ \emph{API, Angular, TypeScript}}{}
\vspace{-8pt}
\resumeItemListStart
  \resumeItem{Created a sleek Angular-based application to help users track their emotional patterns and daily thoughts.}
  \resumeItem{Used TypeScript to build a dynamic mood graph component and sentiment-tagged entry system.}
  \resumeItem{Implemented secure local storage for user data and customizable themes to enhance the journaling experience.}
\resumeItemListEnd 
\vspace{-8pt}

\resumeProjectHeading
{\textbf{\href{https://github.com/PoojasPatel013}{\textcolor{maincolor}{NutriPlanner}}} $|$ \emph{MERN stack}}{}
\vspace{-8pt}
\resumeItemListStart
  \resumeItem{Built a nutrition and meal planning app that tracks macro and micronutrient intake using user-inputted data.}
  \resumeItem{Enabled dynamic meal suggestions based on user goals (e.g., weight loss, gain, keto, vegan) with real-time dashboard.}
  \resumeItem{Used MongoDB for dietary history storage.}
\resumeItemListEnd 
\vspace{-8pt}

\resumeProjectHeading
{\textbf{\href{https://github.com/PoojasPatel013}{\textcolor{maincolor}{Portfolio}}} $|$ \emph{API, React, Tailwind, Email.JS}}{}
\vspace{-8pt}
\resumeItemListStart
  \resumeItem{Developed a modern, responsive personal portfolio site using React and TailwindCSS to showcase projects and skills.}
  \resumeItem{Integrated Email.JS for real-time contact functionality and deployed via Vercel for continuous updates.}
  \resumeItem{Optimized page load and Lighthouse scores through lazy loading and modular architecture.}
\resumeItemListEnd 
\vspace{-8pt}

\resumeProjectHeading
{\textbf{\href{https://github.com/PoojasPatel013}{\textcolor{maincolor}{Client Website}}} $|$ \emph{Gulp, Bootstrap}}{}
\vspace{-8pt}
\resumeItemListStart
  \resumeItem{Designed and maintained a professional website for a client with responsive layout and cross-device compatibility.}
  \resumeItem{Used Gulp to automate build processes, including minification, SCSS compilation, and live reload during development.}
  \resumeItem{Collaborated with stakeholders to meet branding guidelines and deliver SEO-optimized content structure.}
\resumeItemListEnd 
\vspace{-8pt}

\resumeProjectHeading
{\textbf{\href{https://github.com/PoojasPatel013}{\textcolor{maincolor}{Escape Room}}} $|$ \emph{API, SQLite, Socket.io}}{}
\vspace{-8pt}
\resumeItemListStart
  \resumeItem{Created a multiplayer online escape room game where players collaborate in real-time to solve puzzles before time runs out.}
  \resumeItem{Used Socket.io for real-time communication and SQLite for managing game states and user progress.}
  \resumeItem{Designed time-based challenges with increasing complexity and leaderboard tracking.}
  \vspace{-8pt}

         \resumeItemListEnd 
         
   \resumeSubHeadingListEnd
 \vspace{-8pt}

 
%-----------TECHNICAL SKILLS-----------
 \section{Technical Skills}
  \vspace{-8pt}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{\textcolor{sectioncolor}{Programming Languages}}: Python, JavaScript, Java, Kotlin, HTML-CSS \\
    \textbf{\textcolor{sectioncolor}{Frontend}}: React, Angular, Tailwind CSS, Bootstrap, Gulp, Framer \\
    \textbf{\textcolor{sectioncolor}{Backend \& APIs}}: Node.js, Express.js, Flask, Spring Boot, REST APIs \\
    \textbf{\textcolor{sectioncolor}{Databases}}: MongoDB, MySQL, SQLite \\
    \textbf{\textcolor{sectioncolor}{Cloud }}: AWS, Google Cloud, Azure, OCI \\
    \textbf{\textcolor{sectioncolor}{Tools}}: Git, GitHub, Postman, ThunderClient, WordPress, GCP Cloud Shell, Kali Linux \\
    \textbf{\textcolor{sectioncolor}{DevOps}}: AWS, Google Cloud, Azure, OCI, Render, Vercel, GitHub Actions \\
  }}
\end{itemize}


%-----------VOLUNTEER EXPERIENCE-----------
\section{Volunteering/ Service}
\resumeSubHeadingListStart
\resumeSubheading
  {NCC}{Jun 2022 -- Feb 2025}
  {Cadet}{}

  \resumeItemListStart
\resumeItem{Led and participated in social drives including hygiene campaigns and environment awareness programs.}
\resumeItem{Collaborated with fellow cadets, building strong teamwork and crisis response abilities.}
\resumeItem{Developed leadership, communication, and discipline through regular training and drills.}

  \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROFESSIONAL CERTIFICATIONS-----------
\section{Professional Certifications}
\resumeSubHeadingListStart
  \resumeItemListStart
    \resumeItem{\textbf{\href{https://www.credly.com/badges/779092a7-f5ee-4841-87f7-d01d20a46c69/linked_in_profile}{\textcolor{maincolor}{Google Cloud Cloud CyberSecurity}}} – Google Cloud (2025)\\
    Gained understanding of cloud-based threat models, secure architecture design, IAM, VPC firewalls, and data protection strategies on Google Cloud Platform. Strengthened awareness of best practices in cloud networking security. Worked with GCP Cloud Shell.}
    
    \resumeItem{\textbf{\href{https://www.credly.com/badges/3cea21fc-e5a3-4877-be63-54aed5fbb67c/linked_in_profile}{\textcolor{maincolor}{Prompt Design in Vertex-AI Studio}}} – Google Cloud (2025)\\
    Explored prompt engineering techniques for generative AI, including model fine-tuning, chaining logic, and real-world integration of LLMs within GCP’s Vertex AI ecosystem.}
    
    \resumeItem{\textbf{\href{https://forage-uploads-prod.s3.amazonaws.com/completion-certificates/prBZoAihniNijyD6d/oX6f9BbCL9kJDJzfg_prBZoAihniNijyD6d_a8dmNm6w4WyqL3YcY_1736768826973_completion_certificate.pdf}{\textcolor{maincolor}{Advanced Data Structures}}} –  Forage (2024)\\
    Learned to implement and optimize advanced data structures like heaps, trees, and graphs. Applied algorithms for efficient searching, sorting, and data manipulation in coding challenges.}
    
    \resumeItem{\textbf{\textcolor{maincolor}{Computer Networks}} – NPTEL (2020)\\
    Acquired in-depth knowledge of network protocols (TCP/IP, DNS, DHCP), layered architectures (OSI), and routing algorithms. Built a solid foundation in networking principles and packet-level operations. Labs were practiced with Cisco Packet Tracer.}
  \resumeItemListEnd
\resumeSubHeadingListEnd




%-----------Achievements-----------
\section{Achievements}
\resumeSubHeadingListStart
  \resumeItemListStart
    \resumeItem{\textbf{Published Author} - Published Poetry Book with successful market value}
    \resumeItem{\textbf{Novels} - Writer on Amazon Kindle with books published worldwide.}
  \resumeItemListEnd
  
\resumeSubHeadingListEnd

%-----------MEMBERSHIPS-----------
\section{Memberships}
\resumeSubHeadingListStart
  \resumeItemListStart
\resumeItem{\textbf{Google Developer Program} – Member of a global community focused on building scalable applications.}
\resumeItem{\textbf{Google Cloud Innovator Program} – Continuously engaging in Cloud workshops and arcades, working with GCP tools.}
\resumeItem{\textbf{Google Women in Tech} – Actively engaged in workshops promoting diversity in tech.}

    
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
 \resumeEducation
   {Parul University}
   {Bachelor of Technology in Computer Science Engineering}{Vadodara, India}

 \resumeItem{Relevant Coursework: Data Structures, Cloud Computing, Cloud infrastructures, Web development}
  \resumeItem{CGPA: 8.0/10 (First Class with Distinction)}
   
\resumeSubHeadingListEnd

\end{document}